Actuator line modeling of vertical-axis turbines

### 2018-03-31 paper.tex
Fix journal name and correspondence

%=================================================================
\documentclass[journal,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}

@@

% Authors, for the paper (add full first names)
\Author{
    Peter Bachant $^{1,\dagger,\ddagger}$\orcidA{},
    Anders Goude $^{2,\ddagger}$
    and Martin Wosnik $^{1,}$*
}

@@

% Contact information of the corresponding author
\corres{Correspondence: pwbachant@gmail.com}

% Current address and/or shared authorship
% \firstnote{Current address: Affiliation 3}
\secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes

>>>>

%=================================================================
\documentclass[energies,article,submit,moreauthors,pdftex,10pt,a4paper]{mdpi}

@@

% Authors, for the paper (add full first names)
\Author{
    Peter Bachant $^{1}$\orcidA{},
    Anders Goude $^{2,}$
    and Martin Wosnik $^{1,}$*
}

@@

% Contact information of the corresponding author
\corres{Correspondence: martin.wosnik@unh.edu}

% Current address and/or shared authorship
% \firstnote{Current address: Affiliation 3}
% \secondnote{These authors contributed equally to this work.}
% The commands \thirdnote{} till \eighthnote{} are available for further notes
